\chapter{Mission: Datacenter}

\emph{\emph{Datacenter} is a doubles team mission on a~4'x4' play area
  and with~300 army points per side in which the alliances attempt to
  secure Dr Tokh's most valuable data from a major campus computing
  cluster.}

\section{Play Area}

The Deployment Zones are~12'' areas along opposing play area edges.

Nine Server objectives are placed in a grid: Three on the centerline
between the deployment zones, one at the center and the other two~12''
from each edge; and six in two lines of three~8'' from that centerline
in each half of the play area, each with one at the center and the
other two~12'' from each edge.

Each Server is randomly assigned a Data Topic without it being
revealed to either player, via markers placed facedown next to them.
There are three each of three Data Topics: Bio/Xeno, Cyber, and MechE.

\section{Mission Rules}

The standard Initiative Roll may be made against any of your team's
Lieutenants or Special Agents.  Teams whose alliance controls more
Quadrants than their opponents' receive a~+3 MOD to this roll.

%  \href{http://wiki.infinitythegame.com/en/index.php?title=Initiative_and_Deployment}{}

The Connect Objective short skill may be applied to Servers in this
mission.

Players may look at the assigned Data Topic for any Server they have
connected at any time.  In addition, Network Directory tokens earned
by players in the preceding missions may be discarded to look at a
Server's assigned Data Topic (one token per look).  In neither case
are these revealed to the other player.  Players may keep secret notes
about what they have learned of the grid configuration.


\section{Scoring}

Players may score up to~20 objective points via the following
conditions at game end:
\begin{itemize}\shortlist
\item   1pt for each Data Topic of which the player is connected to at least one Server.
\item 2pts for each Data Topic of which the player is connected to the most Servers.
\item   1pt for being connected to at least one Server for each of the three Data Topics.

\item 2pts for each friendly Special Agent in base contact with a
  Server (connected or otherwise).
\item 2pts for each friendly Special Agent wholly in the enemy half of the
  play area.
\item 1pt for each opposing Special Agent in a Null State or eliminated.

% \item 1pt if at least~50\% of your army list by points has survived.
%\item 1pt if more points of the opposing army list have been destroyed.
\end{itemize}
