\clearpage
\chapter{Doubles Rules}

The final mission, Datacenter, is intended to be played as a doubles
game.  Pairs of players within each alliance team up and combine
chosen RECON+ army lists for the final battle.

Partners are chosen at the start of the round by the alliances, they
don't need to be orchestrated in advance.  Their army lists do NOT
need to from the same faction or aligned in any way.  Which army list
to field from their respective remaining pre-selected lists are chosen
by each player at the start of the match, after their partner,
mission, and opponents are determined.

Teammates play together, interleaving orders as they wish in their
active turn, with their models considered friendly but the armies
otherwise separate. For example, this means:

\begin{itemize}
\item Your teammates' models do not trigger AROs from your troopers.
  
\item Your troopers can move through your teammates' as though they
  were your own.
  
\item Both armies have a Lieutenant, a Lieutenant Order, and suffer
  Loss of Lietenant separately.
  
\item Players generate their own Order pool. Orders cannot be shared
  or applied to teammate's troopers.
  
\item Both players get four Command Tokens.  They cannot be shared or
  applied to Tactical Uses on your teammate's troopers.  You also
  cannot move troopers between the two army lists.
  
\item Buffs and abilities like Inspiring Leadership and Chain of
  Command do not carry over.
\end{itemize}

Exceptions to these principles are:

\begin{itemize}
\item Retreat only applies if both armies combined are below quarter
  strength.
\item Players' troopers may Doctor/Medikit, Engineer, and Hack their
  teammates' troopers.  Note that only these abilities may be applied;
  e.g., Sensor is not shared.
\item Only one teammate may invoke a Strategic Use of Command Tokens.
  Nullified orders may be distributed across your opponents as they
  could for combat groups.

\item The Initiative Roll may be made against any of your team's
  Lieutenants or Special Agents.
\end{itemize}
