\chapter{Strike Teams}

Players may bring three RECON+ army lists chosen from the same
faction as their strike team:

% ---up to 150pts each, with limitations on multi-wound models,
% characters, and other properties:

\begin{itemize}
\item You may select up to at most~150 army points per list.

\item Normal rules for SWC, Remotes, etc., apply.

\item Models with troop classification Character that cost more
  than~35pts are not permitted.

\item Only one model with the Impetuous or Extremely Impetuous
  characteristics may be included per every~4 models.  The Frenzy
  characteristic is not limited.

\item Only one model with multiple wounds, structure, or profiles
  (e.g., Symbiont Armor or Transmutation), or V: No Wound
  Incapacitation, may be included per every~4 models.
  
\item Only a single fireteam of any type may be included or active at
  any time.  It may contain a maximum of~3 members and may not be
  reformed to more than that.

\item The entire army list must be organized within a single combat
  group.
\end{itemize}

%\bigskip
%\centerline{\url{http://rocketshipgames.com/infinity/recon+/}}

\missionrule{Mercenaries.}  You may include up to~50 army points of
Mercenary Troops, respecting their AVA, or a single Mercenary Troop
army list selection of any army point value; e.g., you can take one of
the mercenary TAGs despite this limit.\hfill\textit{(this rule
  intentionally varies slightly from standard RECON+)}

\missionrule{Special Agent.}  You must select one 12XP Spec-Ops
trooper as your Special Agent and include it in all of your lists with
exactly the same base profile, weapons, skills, and equipment in each.
The Special Agent is considered to be the same character in each of
your lists; i.e., the campaign progressions detailed later apply to it
regardless of which list you field in each mission.  The army points
for the Special Agent's underlying base profile are to be included
within the 150pt limit for each list but it does not count toward the
AVA of that base profile unit (both these rules are as Army 6
implements for Spec-Ops).  Remember though that Spec-Ops can be part
of Fireteams composed of troops from their base profile's unit.

\missionrule{AVA.}  \underline{You must respect AVA across all 3 lists
  combined!}  The Spec-Ops selection, which implicitly has an AVA of
1, is ignored for this as it is considered the same trooper in each
list---your Special Agent manages to be present at all of your strike
team's critical moments.

\textit{Perhaps the easiest way to ensure you respect AVA across all
  three lists is to build a single list in the army builder of three
  Combat Groups.  Keep each group to at most 150 army points minus the
  base profile cost of your Spec-Ops selection (Army 6 shows a tally
  per group in their header lines).  E.g., a Fusilier Spec-Ops is 10
  army points, so each group has 140pts remaining.  Save that
  mega-list to three other slots, then go into each to delete two
  Combat Groups, flip a trooper to being a Lieutenant, and add your
  Spec-Ops selection.  You do though need to create 3 lists, rather
  than just coming with a 450pt list, to be certain each is within the
  points limit, has a Lieutenant, etc., and you can readily provide
  accurate courtesy lists.}

\missionrule{Strike Team Core.}  One of your lists is to be
designated your Strike Team Core for the event.
