\chapter{Campaign Progression}

All of the following campaign progressions are applied after each of
the first three missions.

\section{Experience}

Your Special Agent and Lieutenant may gain abilities from their
experiences in the firefight.

\missionrule{Special Agent.}  Your Special Agent is permanently
improved by choosing from:

\begin{squishitemize}
\item +1 to one of BS, PH, or WIP
\item +3 to CC
\item +1 to MOV (first value)
\item +1 to ARM (once per campaign)
\item +1 to BTS (once per campaign)
\end{squishitemize}

Remember that the Special Agent is considered the same character in
each of your lists, so these upgrades apply in each subsequent mission
regardless of which list is fielded.

\missionrule{Lieutenant.}  If you won and the Lieutenant on your army
list survived, their BS, PH, or WIP may be permanently improved by~+1,
or their CC by~+3.  Note that this is optional as attributes are
public information, so an improvement reveals your Lieutenant's
identity.  You may not improve a single attribute for any given
Lieutenant more than once per campaign (e.g., after two victories they
could not improve BS twice).

\section{Karma}

If you lost the match, you receive a quantity of Karma tokens equal to
the number of matches you have lost so far in the campaign (including
the just concluded game).  If you lost by~7 or more objective points
then you receive double that quantity.

Karma tokens may be discarded at any point in a later mission to
increase any single die rolled by~+3 (this is not the same as a~+3
MOD, which would affect all dice rolled).  Only one Karma token may be
applied to any given die roll but multiple Karma tokens may be applied
to multiple dice within a roll.

\section{Consequences}

If you play a list other than your Strike Team Core and end any match
with 25\% of the available army points or less remaining (i.e.,~38pts
in RECON+ without Baggage), then that list may not be used again in
the subsequent rounds.  Your Strike Team Core is always available.

Despite being considered a single character, your Special Agent is
available in each round regardless of being a casualty or not in
previous missions or any of your lists becoming unavailable.
