\documentclass{tokh}

\usepackage[colorlinks=true]{hyperref}

\newcommand{\cfbox}[2]{%
    \colorlet{currentcolor}{.}%
    {\color{#1}%
    \fbox{\color{currentcolor}#2}}%
}

\newlength{\currentparskip}
\newlength{\currentparindent}
\newenvironment{stdminipage}[1]
{\setlength{\currentparskip}{\parskip}%
  \setlength{\currentparindent}{\parindent}%
   \begin{minipage}[t]{#1}%
   \setlength{\parskip}{\currentparskip}%
   \setlength{\parindent}{\currentparindent}%
  }
  {\end{minipage}}

\usepackage{xspace}
\newcommand{\missionrule}[1]{\noindent\textbf{#1}\xspace}

\begin{document}
%\squelchbackground
%\includepdf[pages={1},fitpaper,offset=0cm 0cm]{art/cover/tokh-cover.pdf}
%\pagebreak
%\restorebackground

\chapter{Common Rules}

\missionrule{Initiative Roll.}  A standard Initiative Roll determines
Initiative and Deployment, except the Initiative Roll may be made
against either your Lieutenant or your Special Agent.  In addition, in
the Quadrant missions:

\begin{squishitemize}
\item The player that chose the mission receives a +3 MOD.

\item Players whose alliance controls the associated Breach Point or
  Quadrant receive a~+3 MOD.
\end{squishitemize}

\missionrule{Connect Objective.} The Connect Objective short skill may
be applied to objectives in some missions:

% \vspace{-7pt}
\noindent\hfill
{\setlength\fboxrule{2pt}
\cfbox{LimeGreen}{\begin{minipage}{6.5in}
  \colorbox{LimeGreen}{\parbox{\linewidth-2\fboxsep}{\textcolor{White}{\textbf{\large Connect Objective} \hfill Short Skill}}}\\
  \colorbox{SkyBlue}{\parbox{\linewidth-2\fboxsep}{\textcolor{White}{Attack}}}

  \medskip
  \textsc{Requirements}
  \begin{squishitemize}
  \item The user must be a model (not a marker) in base contact with a
    designated objective.
  \end{squishitemize}

  \medskip
  \colorbox{Gray!24}{\begin{minipage}{\linewidth-2\fboxsep}

  \medskip      
      \textsc{Effects}
      \begin{squishitemize}
      \item The user makes a Normal WIP roll with a~-3 MOD to attempt
        connecting the objective.  \emph{Specialist Troops
          automatically pass this roll.}

      \item If successful, the acting player connects to the objective
        (mark it appropriately) and the other player is no longer
        connected if they previously were (remove any marker).
      \end{squishitemize}
    \end{minipage}}
\end{minipage}}}
\hfill\hbox to 0pt{}

\medskip%
\missionrule{Network Terminals.}  The Connect Objective short skill
may be applied to Network Terminals.  At the end of each game round,
if your Special Agent is in base contact with a Network Terminal you
have connected, not a marker, and no enemy troops are in contact, you
receive a Network Directory token.

\missionrule{Experience.}  After each mission, your Special Agent is
permanently improved by choosing from:

\begin{squishitemize}
\item +1 to one of BS, PH, or WIP
\item +3 to CC
\item +1 to MOV (first value)
\item +1 to ARM (once per campaign)
\item +1 to BTS (once per campaign)
\end{squishitemize}

If you won and the Lieutenant on your army list survived, their BS,
PH, or WIP may be permanently improved by~+1, or their CC by~+3.  Note
that this is optional as attributes are public information, so an
improvement reveals your Lieutenant's identity.  You may not improve a
single attribute for any given Lieutenant more than once per campaign
(e.g., after two victories they could not improve BS twice).
  
If you lost the mission, you receive a Karma token.  If you lost by~7
or more objective points then you receive two Karma tokens.  Karma
tokens may be discarded at any point in a later mission to reroll a
single die of yours.  You may not reroll a die that has already been
rerolled.

\missionrule{Endgame.}  All matches end after~3 game turns.
\emph{Retreat!} rules apply as given in the main \emph{Infinity}
rulebook except the game does not end once one player has no models in
play: The remaining player may play out the game turns attempting to
score objectives.

\vfill
\vbox to 0pt{}

\input{mission-breachpoint}

\input{mission-cyber}
\input{mission-bio}
\input{mission-mech}
\input{mission-plant}

\input{mission-datacenter}

\end{document}
